---
title: "Data Description"
author: "Jihyeon Bae"
date: "2024-01-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data Description

This corpus contains 10568 English transcripts of speeches delivered by state representatives of the UN member states at the United Nations General Debate from 1946 until 2022. Text data was made available by Baturo et al. (2017). Original data is in a form of .txt file, each containing speech transcript from one member state in a given year. This RDS data set was generated by executing "rds_generator.R" file to read in all plain text files into a single data frame. File size is $58.61$MB. Alternatively, run "json_converter.R" file to transform plain texts into structured .json files. 

There are four variables in the data. Variable names follow snake case convention. 

-   ccode_iso: three letter character country code based on ISO standards.
-   session: session number of the UN General Debate. The first session was hosted in year 1946. There are 76 session in total.
-   year: Year when session was hosted. Year ranges from 1946 until 2022.
-   text: Speech transcript text before pre-processing.

## Corpus information

```{r, echo=FALSE}
library(stringr)
df<-readRDS("~/Desktop/UNGDC/data/interim/UNGDC.rds")

round((file.info("data/interim/UNGDC.rds")$size/1024)/1024, 2)

df$WordCount <- str_count(df$Text, "\\S+")

round(mean(df$WordCount), 2)
```

Average number of words per text is $2946.91$.

UN General Debate speeches are usually delivered by the head of government or chief foreign minister, and address timely agendas about both international and domestic issues. Statements are formally structured with carefully chosen words. Given that it is a diplomatic forum, words are inflated with positive terms. Statements reflect member state's agenda of priority and position on salient debates at a given year. Below paragraph is an example of an Austrian delegate's speech.

"The principle of the equality of all men has since been expanded by the codifying activities of the United Nations, aimed at preventing all forms of racial discrimination. Discrimination based on the color of the skin or on ethnic origin, such as we find it today in particular in southern Africa, is therefore liable to compromise external peace. The Austrian Government has repeatedly stated that it rejects the concept of apartheid, which is contrary to the Charter, just as it rejects every other political concept based on racial, religious or ethnic discrimination."

## References

Slava Jankin, Alexander Baturo, and Niheer Dasandi. "Words to Unite Nations: The Complete UN General Debate Corpus, 1946-Present." OSF working paper, <https://osf.io/6kty4>

Alexander Baturo, Niheer Dasandi, and Slava Mikhaylov, "Understanding State Preferences With Text As Data: Introducing the UN General Debate Corpus" Research & Politics, 2017.
