---
title: "democracy_dictatorship"
author: "Jihyeon bae"
date: "2023-10-19"
output: 
  html_document:
      number_sections: TRUE
---

```{r setup, include=FALSE}
#just a generic list of packages 
library("pacman")
p_load(plyr, dplyr, ggplot2, tidyverse,haven, stevemisc, magrittr, readxl, 
       #for easy data downloading
       peacesciencer, vdemdata, democracyData, rqog, psData)

```

# Democracy and Dictatorship Dataset

Cheibub's (2004) dataset goes by many different names, as it has been updated by different teams. 
These are all basically the same.
- PACL: as in Przeworski, Alvarez, Cheibub, and Limongi (2000) 
- ACLP: as in Alvarez, Cheibub, Limongi, and Przeworski (1996)
- CGV: as in Cheibub, Gandhi, Vreeland (2004)
- BR: as in Bjørnskov Rode (2020)

## PACL data by Cheibub, Ghandhi, and Vreeland (2004), updated by Bjørnskov and Rode (2020)

```{r}
#I use democracyData package to load PACL data. 
pacl <- democracyData::pacl_update %>% 
  filter(year>=1946) %>%
  dplyr::select(isocode=pacl_update_country_isocode, #three letter ISO code
                gwcode=GWn, #Gleditsch and Ward's countrycode
                ccode=cown, #correlates of war numeric country code, 2016 version
                year, 
                dd_regime=DD_regime, #categorical variable for regime type
                dd_democracy=Democracy) #democracy yes or no 
```

# I'm suspicious how PACL (based on GW) has COW countrycode. 
```{r}
View(pacl[is.na(pacl$ccode)==TRUE,])
#I checked countries that do not match. All make sense except for these cases, where they were simply omitted even when COW does have a corresponding code.

pacl$ccode[pacl$isocode == "HKG"] <- 997 #Hong Kong 
```


### Bonus section
Notice that PACL is based on GW system. Manually check where these mismatches occur, to make sure these are not critical. 
```{r}
#Before merging, check which cells do not match
#"master" dataframe is the main file based on COW list.
View(master %>%
     anti_join(pacl, 
               by=c("country_text_id"="isocode")))
#Some of the country names are different between COW baseline and PACL data. But it's okay as long as key identifiers match.

#This is where a collision between GW and COW shows up.

View(master %>%
     anti_join(pacl, 
               by=c("gwcode"="gwcode")))

#There are 17 cases(German Democratic Republic, Kosovo, Yemen People's Republic) that shows up in COW, but not in PACL data.

master<-left_join(master, pacl,
              by=c('ccode', 'year', 'gwcode'))
```

# Save data as a .csv file
```{r}
#Now that I've checked where mismatches occur, I don't need gwcode and country name.
pacl<-pacl%>%
  select(ccode, year, dd_regime, dd_democracy)

write.csv(pacl, "~/Desktop/UNGDC/data/raw/controls/pacl.csv")
```
