---
title: "Polity"
author: "Jihyeon bae"
date: "2023-10-19"
output: 
  html_document:
      number_sections: TRUE
---

```{r setup, include=FALSE}
#just a generic list of packages 
library("pacman")
p_load(plyr, dplyr, ggplot2, tidyverse,haven, stevemisc, magrittr, readxl, 
       #for easy data downloading
       peacesciencer, vdemdata, democracyData, rqog, psData)

```

# Variables from Polity dataset
```{r}
polity<-democracyData::polity5 %>% #using democracyData package to load dataset
  dplyr::select(polity, 
                polity2, 
                plty_xrcomp=xrcomp, #competitiveness of executive recruitment
                plty_xropen=xropen, #openness of executive recruitment
                plty_xconst=xconst, #executive constraints
                plty_parreg=parreg, #regulation of participation 
                plty_parcomp=parcomp, #competitiveness of participation 
                year, 
                ccode=cown) %>% #COW country index 
  filter(year>=1946)
```

* I'm suspicious how Polity team generated COW code for GW system.
* Below section manually checks just a few ...

```{r, background='#e1f7ba'}
polity_check<-polity%>%
  select(ccode, polity_annual_code)%>% #This is Polity's built-in COW numbering. 
  mutate(check_ccode=countrycode(polity_annual_ccode, "p4n", "cown")) #This is my manual transition.

View(filter(polity, is.na(check_ccode))) 
```

* countries that are unambiguously defined: Serbia, Sudan, Vietnam, USSR
* I see that Polity translated Serbia in GW into Yugoslavia in COW system, USSR into Russia etc. 
* These all make sense!

# Adding on Polity variation from Vreeland (2008)
```{r}
xpolity<-get(load("xpolity_1800-2013.RData")) %>% 
  dplyr::select(ccode, year, 
                xpolity, xconst_xpolity, xrcomp_xpolity, xropen_xpolity) 

polity <- left_join(polity, xpolity,
                    by=c('ccode', 'year')) #Anchoring on original Polity, this adds Vreeland's version

```

# Save this output as a .csv file
```{r}
polity <- write.csv(polity, "~/Desktop/UNGDC/data/raw/controls/polity.csv")
```
