---
title: "ucdp_prio"
author: "Jihyeon bae"
date: "2023-10-21"
output: html_document
---

+ things to change
  - expand 1989:2022
  - add COW country code

```{r setup, include=FALSE}
#just a generic list of packages 
library("pacman")
p_load(plyr, dplyr, tidyverse, haven, stevemisc, magrittr, readxl, 
       #for easy data downloading
       peacesciencer)
```

# UCDP_PRIO Armed Conflict
```{r}
#Manually downloading UCDP PRIO armed conflicts dataset
ucdp_prio<-readRDS("~/Downloads/UcdpPrioConflict_v23_1.rds") 
```


## Compare with the one loaded by peacesciencr package
<!--
temp_for_comparison <- cow %>%
  add_ucdp_acd(type="interstate",#options:extrasystemic, intrastate, II(internationalized intrastate)
               only_wars=FALSE) 
-->

* Using peacesciencer is limited here. It only provides information about the case with the maximum degree of intensity. 


## Modifying peacesciencer package to create own variables
```{r}
ucdp_prio %>%
  filter(year>=1946)%>%
  select(conflict_id, year, gwno_a, gwno_a_2nd, gwno_b, gwno_b_2nd,
         incompatibility, intensity_level, type_of_conflict) -> ucdp_prio

#slicing column 
ucdp_prio %>%
  mutate(gwno_a = strsplit(as.character(gwno_a), ",")) %>%
    unnest(gwno_a) %>%
  mutate(gwno_a_2nd = strsplit(as.character(gwno_a_2nd), ",")) %>%
    unnest(gwno_a_2nd) %>%
  mutate(gwno_b = strsplit(as.character(gwno_b), ",")) %>%
    unnest(gwno_b) %>%
  mutate(gwno_b_2nd = strsplit(as.character(gwno_b_2nd), ",")) %>%
    unnest(gwno_b_2nd) -> ucdp_prio

ucdp_prio %>%
  mutate_at(vars("gwno_a", "gwno_a_2nd", "gwno_b", "gwno_b_2nd"), ~as.numeric(.)) -> ucdp_prio

#Changing numeric code into characters 
ucdp_prio %>%
  mutate(type_of_conflict = case_when(
    type_of_conflict == 1 ~ "extrasystemic",
    type_of_conflict == 2 ~ "interstate",
    type_of_conflict == 3 ~ "intrastate",
    type_of_conflict == 4 ~ "II"
  )) -> ucdp_prio


#Changing numeric code into characters
ucdp_prio %>%
  mutate(incompatibility = case_when(
    incompatibility == 1 ~ "territory",
    incompatibility == 2 ~ "government",
    incompatibility == 3 ~ "both"
  )) -> ucdp_prio


# Convert the dataset to long format
# 4 participants(a, 2nd_a, b, 2nd_b) are counted as "country involved in a conflict"
long_ucdp_prio <- gather(ucdp_prio, key = "variable", value = "value", 
                         -c(conflict_id, year, type_of_conflict, incompatibility,intensity_level))

long_ucdp_prio <- long_ucdp_prio[, c("conflict_id", "year", "value", 
                                     "type_of_conflict", "incompatibility", "intensity_level")]%>%
                  rename(gwcode=value)
```

## Expanding data into a panel
```{r}
# panel data template
## Create a template with all countries and years from 1946 to 2022
country_template <- data.frame(
  gwcode = rep(unique(long_ucdp_prio$gwcode), each = 77),
  year = rep(1946:2022, times = n_distinct(long_ucdp_prio$gwcode))
)

ucdp_prio <- left_join(country_template, long_ucdp_prio, 
                       by = c("gwcode", "year")) %>%
  #Replacing intensity_level=NA into 0.
  replace_na(list(intensity_level = 0))%>%
  #Adding COW code to GW code
  mutate(ccode=countrycode::countrycode(gwcode, "gwn", "cown")) 

ucdp_prio$gwcode[ucdp_prio$gwcode == 816] <- 816 
# Vietnam is coded as Vietnam, Democratic Republic of in GW system.
ucdp_prio$gwcode[ucdp_prio$gwcode == 972] <- 955
# Tonga is coded as 972 in GW, but 955 in COW. 
```
* Warning sign might pop-up, but it's okay. Just 2 cases where GW and COW systems don't match. 
* Mismatches are 816 () and 972 (Tonga). R package `countrycode` failed to capture these two. 

## Creating 4 variables
```{r}
up <- ucdp_prio %>%
  group_by(ccode, year) %>%
  summarize(up_num_conflict=sum(intensity_level== 1),
         up_conflict=ifelse(up_num_conflict>=1, 1, 0),
         up_num_war=sum(intensity_level== 2),
         up_war=ifelse(up_num_war>=1, 1, 0))
```

# Save as a csv file
```{r}
write.csv(up, "~/Desktop/UNGDC/data/raw/controls/ucdp_prio.csv")
write.csv(ucdp_prio, "ucdp_prio_wide.csv")
```

# Bonus: Another easy option is using QOG variables  
```{r}
ucdp<-qog%>%
  filter(year>=1989)%>%
  select(ucdp_type1, ucdp_type2, ucdp_type3, ucdp_type4,
         ccode=ccodecow, year)%>%
  replace_na(list(ucdp_type1= 0))%>% #extrasystemic
  replace_na(list(ucdp_type2= 0))%>% #interstate
  replace_na(list(ucdp_type3= 0))%>% #intrastate
  replace_na(list(ucdp_type4= 0)) %>%#internationalized intrastate
  mutate(up_num_conflict=ucdp_type1+ucdp_type2+ucdp_type3+ucdp_type4) %>%
  mutate(up_conflict=ifelse(up_num_conflict>0,1,0))
```

